{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2021-01-04 documents/supplemental.tex
scd5000 import?

>>>>

many of the base facts - and some of the most useful and simplest methods - are in the early 
papers, and later papers generally just refer to the previous ones. it can be of some use to try to 
find the earliest papers. For instance, when searching for methods for the bacteriophage, lots of 
modern detail-scarce papers appear, but none of the most important Delbruck papers.

"when searching for old papers, use the terminology of the day. millimicrosecond, for instance, for 
nanosecond".
